\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Mohit Singh} % Your name
% if you do not have a website, sub your github instead.
\address{+91 7507203829 \\ Mumbai, India \\
\href{mailto:mohitrajputms123@gmail.com}{mohitrajputms123@gmail.com}} 
\address{ \href{https://www.linkedin.com/in/mohit-singh-bb50a81a5/}{linkedin.com/in/mohit-singh/} \\ \href{https://github.com/anotherwebguy}{github.com/anotherwebguy} \\
\href{https://myportfolio-158b2.web.app}{myportfolio.com}}
%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
% University name, degree, year of graduation, GPA (optional)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{rSection}{Education}

{\bf Mumbai University}, Vidyavardhini's College of Engineering and Technology \hfill {Vasai, India} \\
BE in Computer Science, 9.86 CGPA \hfill {Aug 2019 - Present}

{\bf Viva College}, HSC \hfill {Virar, India} \\
Science, Computer Science, 8.34 \% \hfill {Aug 2017-May 2019}

\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
% What did you do? -> Project goals OR what problem did you solve?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
% Example: 
% + Developed an app for matching mentor and mentees for Android and iOS platform.
% + Successfully matched 85% of the applications and randomized the rest.
% 
% Talk about team work, initiative, soft skills.
%
% Can also include personal projects, competitions, contribution to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{rSection}{Work Experience}
\noindent \textbf{Open Source Contributions - GSSOC} \hfill March 2021 $-$ May 2021 \\
\textit{GirlScript Summer of Code} \hfill Remote
\begin{itemize}
    \setlength\itemsep{-0.7em}
     \item Contributed to 4 open source projects.
     \item Relic Bazaar $|$ Foresttagging $|$ Libro $|$ Batua
 \end{itemize}
 
\noindent \textbf{Software Developer - Android} \hfill Dec 2020 $-$ March 2021 \\
\textit{Innovatiive Creators} \hfill Remote
\begin{itemize}
    \setlength\itemsep{-0.7em}
     \item Innovatiive creators is an tech startup offering digital marketing,app & website development.
     \item Worked on the follwoing apps.
     \item Adhik App $|$ The Tiffinwala co. App $|$ Mango app $|$ The blueplate app $|$ Moviesmatch app
 \end{itemize}
 
\end{rSection} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT
% What did you do?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
%
% Talk about team work, initiative, soft skills.
%
% Can also include personal projects, competitions, contribution to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
\begin{rSection}{PROJECTS}
\vspace{-1.25em}

\item \textbf{Chatfire Chat App} {Dart, Flutter, Firebase} \hfill \href{https://github.com/anotherwebguy/Chat-App-Flutter.git}{View Project}
\vspace{-0.2cm}
\begin{itemize}
    \setlength\itemsep{-0.7em}
     \item Android chat app build in flutter.
     \item Features: Authentication, One to One chat, Status adding 
 \end{itemize}
 
\item \textbf{House Price Prediction } {Python, Machine Learning} \hfill \href{https://github.com/anotherwebguy/House-price-prediction.git}{View Project}
\vspace{-0.2cm}
\begin{itemize}
    \setlength\itemsep{-0.7em}
     \item House price prediction using multiple linear regression through Machine learning in python.
 \end{itemize}
 
\item \textbf{Canteen Automation App} {Dart, Flutter, Firebase} \hfill \href{https://github.com/anotherwebguy/Canteen-Automation-App.git}{View Project}
\vspace{-0.2cm}
\begin{itemize}
    \setlength\itemsep{-0.7em}
     \item A canteen automation app to automate the manual canteen management system
     \item Role based app with admin and user interface to automate manual canteen. 
 \end{itemize}
 
\item \textbf{Captain Bot - Discord Bot} {Python} \hfill \href{https://github.com/anotherwebguy/Captain-Bot.git}{View Project}
\vspace{-0.2cm}
\begin{itemize}
    \setlength\itemsep{-0.7em}
     \item A Discod Bot coded in python using discord.py.
 \end{itemize}

\end{rSection} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Extra Curricular Activities, Leadership, etc 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Other Skills: you can add all your other skills here.
% Continue to keep only relevant skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{SKILLS}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & C/C++, Python, Java, Dart, Javascript, HTML, CSS \\
Frameworks & Flutter, JavaFx, Firebase, Bootstrap \\
Tools & Linux/Windows, Git, VSCode, Eclipse\\
\\
Soft Skills & Time Management, Teamwork, Communication, Problem Solving, Leadership
\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{Profile}
\begin{itemize}
    \setlength\itemsep{-0.7em}
     \item \textbf{Codechef} {anonymous2001}
     \item \textbf{Codeforces} {anonymous2001} 
 \end{itemize}
\end{rSection} 

\begin{rSection}{Achievements}
%\vspace{0}
\begin{itemize}
    \setlength\itemsep{-0.7em}
     \item GirlScript Foundation Education Outreach Scholar.
     \item Swabhav Techlabs Java Scholarship
 \end{itemize}
\end{rSection} 

\end{document}
